{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-02-22 Notebook LaTEX/R-WAPG/paper3.tex
>w<, fixing cringe shit fast

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 90C30, 90C25, 65K10; Secondary 65Y20. 
\noindent{\bfseries Keywords: } 
\\
Convex optimization, Nesterov's acceleration, Proximal gradient, Convergence rate.

@@

            \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. 

@@

    The extended real is defined as $\overline \RR := \RR \cup \{\infty, - \infty\}$. 
    Using $\overline \RR$ we model a general convex function $g: \RR^n \rightarrow \overline{\RR}$ as a function on $\RR$.  
    The domain has the definition $\dom(g) := \{x \in \RR^n : g(x) < \infty\}$. 
    A proper function $g$ means that there exists some $x \in \dom(g)$ such that $g(x) > -\infty$. 

@@

        T_Ly &= \argmin_{x \in \RR^n} \left\lbrace

@@

        \right\rbrace = [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f], 

@@

        \defeq f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 

@@

        For simplicity of notations, we write $T$ for $T_L$. 

@@

        $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is $L + \mu$ strongly convex by Assumption \ref{ass:smooth-nsmooth-additive} and its definition. 
        We see that it admits quadratic growth over the minimizer $Ty$ therefore for all $x \in \RR^n$ it follows that: 

@@

            \frac{L + \mu}{2}\Vert x - Ty\Vert^2

@@

            - \frac{L + \mu}{2}\Vert x - Ty\Vert^2

@@

            + D_f(Ty, y). \quad \text{By $\mu \ge 0$}

@@

\section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
    The goal of this section is to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
    \par 
    Definition \ref{def:stepwise-wapg} describes one iteration of the R-WAPG algorithm. 
    It defines the procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
    Proposition \ref{prop:stepwise-lyapunov} states the inequality \eqref{ineq:stepwise-lya-2}  of a decreasing quantity involving $F(x_k), F(x_{k + 1})$ at each iteration.
    \par
    The assumption below is crucial to describing the convergence rate of the R-WAPG and it requires the convexity assumption on $F$. 
    \begin{assumption}
        Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
        \begin{align}
            g_k &\defeq L(y_k - T_L y_k), 
            \label{eqn:grad-map}
            \\
            l_F(x; y_k) &\defeq F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
            \label{eqn:lower-linearization}
            \\
            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
            \label{eqn:regret}
        \end{align}
        Observe that by convexity of $F$, $\epsilon_k \ge 0$ for all $x_k, L > 0$. 
        To see, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$ which gives: 
        \begin{align*}
            F(x_k) - F(T_Ly_k)
            - \langle L(y_k - T_Ly_k),x_k - y_k \rangle
            - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
            - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
            &\ge 0
            \\
            \iff 
            F(x_k) - F(T_Ly_k)
            - \langle g_k,x_k - y_k \rangle
            - \frac{1}{2L}\Vert g_k\Vert^2
            &\ge 0. 
        \end{align*}
    \end{assumption}

@@

        On the first equality \eqref{eqn:Q1}, we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then grouped $y_k$. 
        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the denominator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$. 

@@

@@

        On the second equality that follows, we substituted $\hat\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$ given by \eqref{eqn:stepwise-wapg-eqn1}. 
        Finally, we start by considering the LHS of \eqref{eqn:Q3} and it follows that: 

@@

        Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfies Definition \ref{def:stepwise-wapg}. 
        Define: 

@@

        Now, it remains to show \eqref{eqn:stepwise-lya-proof-step-1}, \eqref{eqn:stepwise-lya-proof-step-2}, \eqref{eqn:stepwise-lya-proof-step-3}. 
        \par\noindent

@@

        \begin{align}\label{eqn:stepwise-lya-proof-eqn3}

@@

@@

@@

    \end{proof}
    \begin{remark}
        Given $y_k$, we can choose to increase $\mu_\kappa = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2 \ge \mu$ which also works on \eqref{ineq:stepwise-lya-proof-ineq4}.
        This is true by the intermediate steps taken to prove Theorem \ref{thm:prox-grad-ineq}. 
        $\mu$ is a pessimistic choice for the inequality above. 
        But in general the choice of $\mu$ remains the strong convexity modulus or equivalently, any value that is smaller than the true strong convexity constant for claiming the convergence rate for all initial guesses. 
    \end{remark}

@@

            For $k=1, 2, 3, \cdots$
                \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
                \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 

@@

                g_k &= \mathcal G_L y_k, 

@@

                x_{k + 1} &= T_L y_k. 

@@

@@

        The choice of $\rho_k = 1$ reproduces traditional choice of sequences for the APG algorithm. 
        The above claim showed that there exists $\rho_k > 1$, or $\rho_k < 1$ where convergence of $F(x_k) - F(x^*)$ remains possible. 

@@

    Sometimes the same algorithm include two iterates $(x_k, y_k)$, sometimes they inlcude three iterates $(x_k, y_k, z_k)$. 

@@

    These forms are equivalent and they are crucial for proving the convergence of existing variants found in the literatures in the upcoming Section \ref{sec:rwapg-literatures}. 

@@

    To start, the following proposition on ``abstract similar triangle form'' were made to simplify arguments and notations to make nicer proofs. 

@@

@@

            - (y_k - L^{-1}\mathcal G_Ly_k)

@@

            + L^{-1}\mathcal G_Ly_k

@@

@@

                        v_{k + 1} + 

@@

@@

@@

                    & y_k = 

@@

            (3.1, 4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}.

@@

                    & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 

@@

                    y_{k + 1} = 

@@

            See Theorem \ref{thm:r-wapg-on-cham-doss} and Lemma \ref{lemma:inverted-fista-seq} to see a specific choice of $(\alpha_k)_{k \ge0}, (\rho_k)_{ k\ge 0}$ such this equivalent form of R-WAPG is in fact two possible variants of the FISTA algorithm.

@@

    \subsection{Proofs of equivalent representations of R-WAPG}
        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\

@@

        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\

@@

            We shall verify the hypothesis that $L\delta_k = 1 + \tau_k + \xi_k$ later, for now substituting $\xi_k$ gives: 

@@

        \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}

@@

            The coming parts simplifies $y_k$ firstly for $k = 1$, then for all $k \ge 2$. 

@@

            For all $k\ge 1$, substitute RHS of \eqref{eqn:third-eqv-repr-proof-step1} yields: 

@@

                y_1 &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L\alpha_1)x_1)
                &= (L - \mu)^{-1}(L(\alpha_1 - \mu)x_1 + (L - L \alpha_1)x_1)

@@

                $\mathcal O \left(\max(1 - \alpha, 1 - \mu/(\alpha L))^{k} \right)$\\

@@

    The lemma follows characterizes momentum sequences in the literatures using Definition \ref{def:rwapg-seq}. 

@@

        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 

@@

            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$

@@

            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & \mu = 0 \text{ assumed } 

@@

            &  \rho_k \ge 1

@@

        When $k = 0$, it has $\alpha_0 = 1$. 
        By definition of $\rho_0$ we have 
            \alpha_1^2 &= 
            (1 - \alpha_1)\alpha_0^2\rho_0 \underset{\mu = 0}{=}
            \frac{\alpha_1^2}{\alpha_0^2(1 - \alpha_1)}(1 - \alpha_1)\alpha_0^2 = \alpha_1^2. 

@@

        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chambolle, Dossal \cite{chambolle_convergence_2015}. 

@@

                & \theta_{t + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),

@@

                \frac{a}{k + 1}

@@

            \item The momentum terms $\theta_{t + 1}$ in Definition \ref{def:r-wapg-momentum-form}, which we denoted by $\theta$ is the constant:\\ $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$
            \item When $r = 1$, $\theta = (1- \sqrt{q})(1 + \sqrt{q})^{-1}$. 
            \item For all $r \in \left(1, \sqrt{q^{-1}}\right)$, $\rho > 1$; for all $r \in \left(\sqrt{q}, 1\right]$ $\rho \le 1$. 
            \item For all $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, $\max(\rho, 1)(1 - \alpha) = \max\left(1 - r\sqrt{q}, 1 - r^{-1}q\right)$. 

@@

        Therefore, $\alpha_k \in (\mu/L, 1)$. 

@@

        Finally, to show (v), we consider by cases: 
            \item[Case A:] When $r \in \left(1, \sqrt{q^{-1}}\right)$, we have $\rho > 1$ by (iii), meaning that $1 - r^{-1}\sqrt{q} > 1 - r \sqrt{q}$. $\rho > 1 \implies \max(\rho, 1) = \rho$ hence 
                    \max(\rho, 1)(1 - \alpha) &= \rho(1- \alpha)
                    = \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}(1 - r \sqrt{q}) = 1 - r^{-1}\sqrt{q}. 
                In this case, the larger one of the two values: $\left\lbrace1 - \rho^{-1}\sqrt{q}, 1 - r\sqrt{q}\right\rbrace$ is taken. 
            \item[Case B:] When $r \in \left(\sqrt{q}, 1\right]$, we have $\rho \le 1$ by (iii); hence $1 - r^{-1}\sqrt{q} \le 1 - r \sqrt{q}$ and $\max(1,\rho) = 1$ therefore: 
                \max(1, \rho)(1 - \alpha) = (1 - \alpha) = 1 - r \sqrt{q}. 
            Once again, the larger one of the quantity: $1 - r \sqrt{q}$ among $\{1 - r^{-1}\sqrt{q}, 1 - r\sqrt{q}\}$ is taken. 
        Therefore, for all vales of $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$ are completed by cases: (A), (B).
        The largest of the value among $\{1 - r \sqrt{q}, 1 - r^{-1}\sqrt{q}\}$ is always taken. 
        Therefore, it has: 
            \max(1, \rho)(1 - \alpha) = \max\left(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q}\right). 

@@

    \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
        Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Lemma \ref{lemma:constant-rwapg-seq}.
        Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, let $\alpha_k := \alpha = r \sqrt{q}$ be the constant R-WAPG sequence. 
        Consider the algorithm with a constant momentum specified by the following: 
        \begin{tcolorbox}
            Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$. 
            \\
            Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update: 
            \begin{align*}
                &x_{k + 1} = y_k + L^{-1}\mathcal G_L y_k, 
                \\
                & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k). 
            \end{align*}
        \end{tcolorbox}
        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k\right)$. 
    \end{theorem}
    \begin{proof}
        The constant sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence by Lemma \ref{lemma:constant-rwapg-seq}. 
        The algorithm presented here is the same as the R-WAPG momentum form as given by Definition \ref{def:r-wapg-momentum-form} because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form} by (ii) in Lemma \ref{lemma:constant-rwapg-seq}. 
        Then, Proposition \ref{prop:wapg-convergence} applies and it follows that: 
        \begin{align*}
            & F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &= 
            F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert x_{k + 1}  - x^* + (\alpha^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
            \\
            &\le 
            \left(
                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
            \right)
            \left(
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \left(
                \prod_{i = 1}^{k - 1} \max(1, \rho)(1 - \alpha)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
            \right). 
            & \text{Lemma \ref{lemma:constant-rwapg-seq} (v)}
        \end{align*}
        Going from the second last to the last equality, we used the initialization condition $y_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, therefore it has $v_1 = x_1$. 
    \end{proof}
    \begin{remark}
        When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of Beck's book \cite{beck_first-order_2017}. 
    \end{remark}

@@

        \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
        \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}

@@

            \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
            \WHILE{$L/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
                \STATE{$L:= 2L$;}
                \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }

@@

            \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}

@@

            \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}

@@

                (\alpha_k^2 - q + 2)^2 + 2q - 4

@@

                \NOG

@@

                    \caption{Single lasso experiment plot of $\delta_k$ with.  }

>>>>

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 90C30, 90C25, 65K10; Secondary 65Y20. 
\\{\bfseries Keywords: } 
Convex optimization, Nesterov's acceleration, Proximal gradient, Convergence rate.

@@

            \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. The extended real is defined as $\overline \RR := \RR \cup \{\infty\}$. 

@@

@@

        T_L(y) &:= \argmin_{x \in \RR^n} \left\lbrace

@@

        \right\rbrace = [I + L^{-1}\partial g]^{-1}\circ [I - L^{-1}\nabla f](y), 

@@

        \defeq (x, y)\mapsto f(x) - f(y) - \langle \nabla f(y), x - y\rangle. 

@@

        For simplicity, we write $T$ for $T_L$. 

@@

        $\widetilde{\mathcal M}^{L^{-1}}(\cdot; y)$ is $L$ strongly convex by Assumption \ref{ass:smooth-nsmooth-additive} and its definition. 
        We see that it admits quadratic growth over the minimizer $Ty$, therefore for all $x \in \RR^n$ it follows that: 

@@

            \frac{L}{2}\Vert x - Ty\Vert^2

@@

            - \frac{L}{2}\Vert x - Ty\Vert^2

@@

            + D_f(Ty, y).

@@

\section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
    The goal of this section is to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
    \par 
    Definition \ref{def:stepwise-wapg} describes one iteration of the R-WAPG algorithm. 
    It defines the procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
    Proposition \ref{prop:stepwise-lyapunov} states the inequality \eqref{ineq:stepwise-lya-2}  of a decreasing quantity involving $F(x_k), F(x_{k + 1})$ at each iteration.
    \par
    The assumption below is crucial to describing the convergence rate of the R-WAPG and it requires the convexity assumption on $F$. 
    \begin{assumption}
        Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
        \begin{align}
            g_k &\defeq L(y_k - T_L(y_k)), 
            \label{eqn:grad-map}
            \\
            l_F(x; y_k) &\defeq F(T_L(y_k)) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
            \label{eqn:lower-linearization}
            \\
            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
            \label{eqn:regret}
        \end{align}
        % To see $\epsilon_k \ge 0$, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$, by the definition $g_k = L(y_k - T_L(y_k))$ it has: 
        % \begin{align*}
        %     F(x_k) - F(T_L(y_k))
        %     - \langle L(y_k - T_L(y_k)),x_k - y_k \rangle
        %     - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
        %     - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
        %     &\ge 0
        %     \\
        %     \iff 
        %     F(x_k) - F(T_L(y_k))
        %     - \langle g_k,x_k - y_k \rangle
        %     - \frac{1}{2L}\Vert g_k\Vert^2
        %     &\ge 0. 
        % \end{align*}
    \end{assumption}

@@

        % On the first equality \eqref{eqn:Q1}, we multiplied both side of the equation by $\hat\gamma_{k + 1}/\alpha_k \gamma_k$ and then grouped $y_k$. 
        % The last equality comes by multiplying both the numerator and denominator by $\hat \gamma_{k + 1}$, then simplifies the denominator by rearranging \eqref{eqn:stepwise-wapg-eqn1} into $\hat \gamma_{k + 1} + \alpha_k \gamma_k = \gamma_k + \alpha_k \mu$. 
        % \par

@@

            & \text{by \eqref{eqn:stepwise-wapg-eqn1}}

@@

        % On the second equality that follows, we substituted $\hat\gamma_{k + 1} = (1 - \alpha_k)\gamma_k + \alpha_k \mu$ given by \eqref{eqn:stepwise-wapg-eqn1}. 
        Using \eqref{eqn:Q1}, \eqref{eqn:Q2}, we can show \eqref{eqn:Q3}. 
        Indeed,

@@

        Given any $v_k, x_k$ and $\gamma_k > 0$ and $v_{k + 1}, x_{k + 1}, y_k, \hat \gamma_{k + 1}, \alpha_k$ that satisfy Definition \ref{def:stepwise-wapg}. 
        With $\epsilon_k$ given by \eqref{eqn:regret}, define: 

@@

@@

@@

        \end{split}\nonumber

@@

        \end{split}\label{eqn:stepwise-lya-proof-eqn3}

@@

    \end{proof}
    \begin{remark}
        Given $y_k$, we can choose to increase $\mu_k = 2D_f(x^*, y_k)/\Vert y_k - x^*\Vert^2 \ge \mu$ which also works on \eqref{ineq:stepwise-lya-proof-ineq4}.
        This is true by the intermediate steps taken to prove Theorem \ref{thm:prox-grad-ineq}. 
        $\mu$ is a pessimistic choice for the inequality above. 
        But in general the choice of $\mu$ remains the strong convexity modulus or equivalently, any value that is smaller than the true strong convexity constant for claiming the convergence rate for all initial guesses. 
    \end{remark}

@@

            For $k=1, 2, 3, \ldots$
                \gamma_k &\defeq \rho_{k -1}L\alpha_{k - 1}^2, 
                \hat \gamma_{k + 1} & \defeq (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
                y_k &\defeq 

@@

                g_k &\defeq \mathcal G_L (y_k), 
                v_{k + 1} &\defeq 

@@

                x_{k + 1} &\defeq T_L y_k. 

@@

        Let $\epsilon_k$ be given by \eqref{eqn:regret}. 

@@

        The choice of $\rho_k = 1$ reproduces traditional choice of sequences for the Accelerated Proximal Gradient (APG) algorithm. 
        % The above claim showed that there exists $\rho_k > 1$, or $\rho_k < 1$ where convergence of $F(x_k) - F(x^*)$ remains possible. 

@@

    Sometimes the same algorithm include two iterates $(x_k, y_k)$, sometimes they include three iterates $(x_k, y_k, z_k)$. 

@@

    These forms are equivalent, and they are crucial for proving the convergence of existing variants found in the literatures in the upcoming Section \ref{sec:rwapg-literatures}. 

@@

    To start, the following proposition on ``abstract similar triangle form'' were made to simplify arguments and notations and to make cleaner proofs. 

@@

        \begin{align}\label{eqn:abs-st-key}

@@

            - (y_k - L^{-1}\mathcal G_L(y_k))

@@

            + L^{-1}\mathcal G_L(y_k)

@@

                    & y_{k} \defeq 

@@

@@

                    & x_{k + 1} \defeq 

@@

                    & v_{k + 1} \defeq 

@@

                    & y_k \defeq 

@@

            Sections (3.1), (4.1) in Lee et al. \cite{lee_geometric_2021} and Ahn and Sra \cite{ahn_understanding_2022}.

@@

                    & x_{k + 1} \defeq y_k - L^{-1}\mathcal G_Ly_k, 

@@

                    y_{k + 1} \defeq 

@@

            See Theorem \ref{thm:r-wapg-on-cham-doss} and Lemma \ref{lemma:inverted-fista-seq} for a specific choice of $(\alpha_k)_{k \ge0}, (\rho_k)_{ k\ge 0}$ such that this equivalent form of R-WAPG is in fact two possible variants of the FISTA algorithm.

@@

    \subsection{Derivations of equivalent representations of R-WAPG}
        \begin{proposition}[R-WAPG intermediate form]\label{prop:wapg-first-equivalent-repr}\;\\

@@

        \begin{proposition}[R-WAPG similar triangle form]\label{prop:wagp-st-form}\;\\

@@

            We shall verify the hypothesis that $L\delta_k = 1 + \tau_k + \xi_k$ later.
            Substituting $\xi_k$ into \eqref{eqn:abs-st-key} gives: 

@@

        \begin{proposition}[R-WAPG momentum form]\label{prop:r-wapg-momentum-repr}

@@

            Simplifying $y_k$ firstly for $k = 1$, then for all $k \ge 2$. 

@@

            For all $k\ge 1$, substitute RHS of \eqref{eqn:third-eqv-repr-proof-step1} into the above yields: 

@@

                y_1 &= (L - \mu)^{-1}((L\alpha_1 - \mu)x_1 + (L - L\alpha_1)x_1)
                &= (L - \mu)^{-1}((L\alpha_1 - \mu)x_1 + (L - L \alpha_1)x_1)

@@

                $\mathcal O \left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^{k}\right)$\\

@@

    The lemma follows characterizes momentum sequences in Chambolle and Dossal \cite{chambolle_convergence_2015} using Definition \ref{def:rwapg-seq}. 

@@

        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 

@@

            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$.

@@

            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & 
            (\mu = 0 \text{ assumed } )

@@

            &  (\rho_k \ge 1)

@@

        We need to verify the base case for $k = 0$. 
        Since $\alpha_0 = 1$, it has: 
            \alpha_1^2 &= (1 - \alpha_1)\rho_0\alpha_0^2
            &\ge (1 - \alpha_1)\alpha_0^2
            &= (1 - \alpha_1)
            1 &\ge \alpha_1^{-2} - \alpha_1^{-1}. 

@@

        The sequence $t_k$ is exactly the same as in Chambolle, Dossal \cite[Theorem 3.1, 8]{chambolle_convergence_2015}. 

@@

                & \theta_{k + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1),

@@

                \frac{a}{k + a}

@@

            \item The momentum term $\theta_{k + 1}=\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1})$ in Definition \ref{def:r-wapg-momentum-form}, denoted by $\theta$ is the constant: $\theta = (1 - r^{-1}\sqrt{q})(1 - r\sqrt{q})(1- q)^{-1}$
            \item When $r = 1$, we have $\theta = (1- \sqrt{q})(1 + \sqrt{q})^{-1}$. 
            \item For all $r \in \left(1, \sqrt{q^{-1}}\right)$, we have $\rho > 1$; for all $r \in \left(\sqrt{q}, 1\right]$ we have $\rho \le 1$. 
            \item For all $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, the equality $\max(\rho, 1)(1 - \alpha) = 1 - \min\left(\frac{\mu}{\alpha L}, \alpha\right)$ holds. 

@@

        Therefore, $\alpha_k = \alpha \in (\mu/L, 1)$. 

@@

        Finally, to show (v), consider substituting $\rho, \alpha$ in terms of $r$: 
            \max(\rho, 1)(1 - \alpha) &= 
            \max(\rho(1 - \alpha), (1 - \alpha))
            &= \max\left(
                \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}(1 - \alpha), (1 - \alpha)
            \max\left(
                \frac{1 - r^{-1}\sqrt{q}}{1 - r \sqrt{q}}(1 - r\sqrt{q}), (1 - r\sqrt{q})
            &= \max\left(1 - r^{-1}\sqrt{q}, 1 - r \sqrt{q}\right)
            &= 1 - \min(\sqrt{q}r^{-1}, r\sqrt{q}). 
        We used the fact that $(1 - \alpha) > 0, \sqrt{q} > 0$ and (i) for substituting $\rho$. 
        Now, by definition $r = \alpha/\sqrt{q}$ and $q = \mu/L$, it can be represented by
            1 - \min\left(
                \sqrt{q}\left(\frac{\sqrt{q}}{\alpha}\right), \alpha
            \right) &=
            1 - \min\left(
                q/\alpha, \alpha
            \right) = 
            1 - \min\left(\frac{\mu}{\alpha L}, \alpha\right). 

@@

    \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
        Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Lemma \ref{lemma:constant-rwapg-seq}.
        Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, let $\alpha_k := \alpha = r \sqrt{q}$ be the constant R-WAPG sequence. 
        Consider the algorithm with a constant momentum specified by the following: 
        \begin{tcolorbox}
            Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$. 
            \\
            Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update: 
            \begin{align*}
                &x_{k + 1} = y_k + L^{-1}\mathcal G_L y_k, 
                \\
                & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k). 
            \end{align*}
        \end{tcolorbox}
        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^k\right)$. 
    \end{theorem}
    \begin{proof}
        The constant sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence by Lemma \ref{lemma:constant-rwapg-seq}. 
        The algorithm presented here is the same as the R-WAPG momentum form as given by Definition \ref{def:r-wapg-momentum-form} because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form} by (ii) in Lemma \ref{lemma:constant-rwapg-seq}. 
        Then, Proposition \ref{prop:wapg-convergence} applies,and it follows that: 
        \begin{align*}
            & F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &= 
            F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert x_{k + 1}  - x^* + (\alpha^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
            \\
            &\le 
            \left(
                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
            \right)
            \left(
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \left(
                \prod_{i = 1}^{k - 1} \max(1, \rho)(1 - \alpha)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \left(1 - \min\left(\frac{\mu}{\alpha L}, \alpha\right)\right)^k
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
            \right). 
            & \text{Lemma \ref{lemma:constant-rwapg-seq} (v)}
        \end{align*}
        Going from the second last to the last equality, we used the initialization condition $y_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, therefore it has $v_1 = x_1$. 
    \end{proof}
    \begin{remark}
        When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of Beck's book \cite{beck_first-order_2017}. 
        The above theorem gives convergence rate for a much relax choice of momentum parameter $\theta$ generalizing the convergence of constant step size FISTA to all convex stronlgy convex function and all possible $\alpha_k \in (\mu/L, 1)$. 
        In addition, the convergence claim of R-WAPG holds for any $\mu$ smaller than the strong convexity modulus of $f$ that is not zero making the bounds $r \in (\sqrt{q}, \sqrt{q^{-1}})$ looser. 
    \end{remark}

@@

        \STATE{\textbf{Input: } $f, g, L > \mu \ge 0, x_0 \in \RR^n, N \in \N$}
        \STATE{\textbf{Initialize: }$y_0 := x_0;L_0 := 1; \mu_0 := 1/2; \alpha_0 = 1$;}

@@

            \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$;}
            \WHILE{$L_k/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
                \STATE{$L_k:= 2L_k$;}
                \STATE{$x^+ = [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$; }

@@

            \STATE{$\alpha_{k + 1} := (1/2)\left(\mu_k/L_k - \alpha_{k}^2 + \sqrt{(\mu_k/L_k - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}

@@

            \STATE{$\mu_k := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}

@@

                (\alpha_k^2 - q + 2)^2 + 4q - 4

@@

                \NOG_k

@@

                    \caption
